Supporting Information

### 2018-03-03 SupportingInformation.Rmd
changes in some chunks for caching

seed<-101
families<-c(1,3:10,13,14,16:20)
#A function needed for caching
mtime <- function(files)
{
  lapply(Sys.glob(files),function(x) X =   
          file.info(x)$mtime)
}
source("getcopula.R")
source("OurBiCopSelect.R")
source("FittingCopula_selective_loc.R")
source("aphid_data_calling.R")
source("plankton_north_sea_data_calling.R")
source("NonParamStat.R")
source("copsurrog2d.R")
```

@@

#### stat_TlTu

```{r stat_TlTu, echo=F}
fig_nums("stat_TlTu",display=F)
```
![schematic diagram for stat_TlTu](./TlTu.jpg){ width=30%, height=30% }

This statistic is an alternative kind of the previous statistics. Here, to measure tail dependence between two marginal distributions, we will calculate our statistics on left and right side of $vi+vj=1$ line [see `r fig_nums("stat_TlTu",display="c")`] of the unit square box. First, we take $Il$, the ratio of number of points within the shaded lower triangle and the number of points lie on the left side of $vi+vj=1$ line. This $Il$ is a function of 
box-corner to the box-diagonal distance $h$ which has range from $0$ to $\sqrt2/2$ (= half of the length of the box-diagonal). Thus $Il$ also lies in between the same range [$0,1$]. Similarly, we calculate $Iu(h)$ for region $vi+vj>1$. Usual independent standard $Ii(h)$ represents the ratio of one shaded triange and the area of right angled isosceles triangle of unit side. Now, we want to measure that how much $Il(h)$ and $Iu(h)$ deviate from the standard $Ii(h)$ line when they are plotted against $h$. Their deviations $Tl$ and $Tu$, representing our statistics to measure lower and upper tail dependence, are given by;

\begin{equation}\label{eq.Tl}
   Tl = \int_0^{\sqrt2/2} \left[ Il(h) - Ii(h) \right] \,dh
\end{equation}

\begin{equation}\label{eq.Tu}
   Tu = \int_0^{\sqrt2/2} \left[Iu(h) - Ii(h) \right] \,dh
\end{equation}

According to this statistic a copula with more lower tail dependence should have positive $(Tl-Tu)$ value whereas a copula with negative $(Tl-Tu)$ represents more upper tail dependence. A copula with equal $Tl$ and $Tu$ value is considered as a member of symmetric copula family with no tail-dependence.

@@

### Non-paramtric analysis of tail dependence
<!--Do the intensive part of the analysis-->
```{r stat_soilCN, echo=F, cache=T, cache.extra=list(seed,v,mtime("CopulaFunctions.R"),mtime("copsurrog2d.R"),mtime("NonParamStat.R"))}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_soilCN/"

#get the stats for the real data
stat_soilCN<-copsync(v) 
saveRDS(stat_soilCN,paste(resloc,file="stat_soilCN.RDS",sep=''))
sCN<-stat_soilCN[c(2:5,7,8,10:13)]
stat<-unlist(sCN)
stat<-c(stat[1:4],unname(stat[3]-stat[4]),stat[5:6],unname(stat[5]-stat[6]),stat[7:8],unname(stat[7]-stat[8]),stat[9:10],unname(stat[10]-stat[9]))
names(stat)[c(5,8,11,14)]<-c("Corl-Coru","Pl-Pu","Tl-Tu","D2u-D2l")

#get surrogates and get stats for them, preserving kendall
cop<-normalCopula(.5,2)
numsurrog<-1000
surv<-copsurrog2d(v,cop,"kendall",numsurrog)
statsurr_k<-matrix(NA,length(stat),numsurrog)
rownames(statsurr_k)<-names(stat)
for (counter in 1:dim(surv)[3])
{
  h<-copsync(surv[,,counter])
  h<-unlist(h[c(2:5,7,8,10:13)])
  h<-c(h[1:4],h[3]-h[4],h[5:6],h[5]-h[6],h[7:8],h[7]-h[8],h[9:10],h[10]-h[9])
  statsurr_k[,counter]<-unname(h)
}

#same, preserving spearman
surv<-copsurrog2d(v,cop,"spearman",numsurrog)
statsurr_s<-matrix(NA,length(stat),numsurrog)
rownames(statsurr_s)<-names(stat)
for (counter in 1:dim(surv)[3])
{
  h<-copsync(surv[,,counter])
  h<-unlist(h[c(2:5,7,8,10:13)])
  h<-c(h[1:4],h[3]-h[4],h[5:6],h[5]-h[6],h[7:8],h[7]-h[8],h[9:10],h[10]-h[9])
  statsurr_s[,counter]<-unname(h)
}
```

@@

```{r stat_aphid_count, echo=F, cache=T, cache.extra=list(seed,data_aphid_count)}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_aphid_count/"

@@

```{r count_Tl-Tu,echo=F}
fig_nums("count_Tl-Tu",display=F)
```
![Tl-Tu vs. Distance plot for aphid-count showing lower tail dependence](./Results/stat_results/stat_aphid_count/Sp_10_Tl-Tu_vs_D.pdf){ width=50%, height=50% }

@@

```{r count_D2u/D2l,echo=F}
fig_nums("count_D2u/D2l",display=F)
```
![D2u/D2l vs. Distance plot for aphid-count showing lower tail dependence](./Results/stat_results/stat_aphid_count/Sp_10_D2u_by_D2l_vs_D.pdf){ width=50%, height=50% }

@@

```{r stat_aphid_ff, echo=F, cache=T, cache.extra=list(seed,data_aphid_ff)}
set.seed(seed)
resloc<-"./Results/stat_results/stat_aphid_ff/"

@@

```{r ff_Tl-Tu,echo=F}
fig_nums("ff_Tl-Tu",display=F)
```
![Tl-Tu vs. Distance plot for aphid-firstflight showing upper tail dependence](./Results/stat_results/stat_aphid_ff/Sp_11_Tl-Tu_vs_D.pdf){ width=50%, height=50% }

@@

```{r ff_D2u/D2l,echo=F}
fig_nums("ff_D2u/D2l",display=F)
```
![D2u/D2l vs. Distance plot for aphid-firstflight showing upper tail dependence](./Results/stat_results/stat_aphid_ff/Sp_11_D2u_by_D2l_vs_D.pdf){ width=50%, height=50% }

@@

### Non-paramtric analysis of tail dependence
```{r stat_plankton_north_sea, echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea)}
set.seed(seed)
resloc<-"./Results/stat_results/stat_plankton_north_sea/"

@@

```{r pns_Tl-Tu,echo=F}
fig_nums("pns_Tl-Tu",display=F)
```
![Tl-Tu vs. Distance plot for Plankton_north_sea showing lower tail dependence](./Results/stat_results/stat_plankton_north_sea/Sp_16_Tl-Tu_vs_D.pdf){ width=50%, height=50% }

@@

```{r pns_D2u/D2l,echo=F}
fig_nums("pns_D2u/D2l",display=F)
```
![D2u/D2l vs. Distance plot for Plankton_north_sea showing lower tail dependence](./Results/stat_results/stat_plankton_north_sea/Sp_16_D2u_by_D2l_vs_D.pdf){ width=50%, height=50% }

>>>>

seed<-101
families<-c(1,3:10,13,14,16:20)
#A function needed for caching
mtime <- function(files)
{
  lapply(Sys.glob(files),function(x) X =   
          file.info(x)$mtime)
}
source("getcopula.R")
source("OurBiCopSelect.R")
source("FittingCopula_selective_loc.R")
source("aphid_data_calling.R")
source("plankton_north_sea_data_calling.R")
source("NonParamStat.R")
source("copsurrog2d.R")
source("CopulaFunctions_flexible.R")
```

@@

@@

### Non-paramtric analysis of tail dependence
<!--Do the intensive part of the analysis-->
```{r stat_soilCN, echo=F, cache=T, cache.extra=list(seed,v,mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_soilCN/"

stat_soilCN<-stat_flexible_fn(m=v,lb=0,ub=0.1)
saveRDS(stat_soilCN,paste(resloc,file="stat_soilCN.RDS",sep=''))

stat<-unlist(stat_soilCN)
stat<-c(stat[1:4],unname(stat[3]-stat[4]),stat[5:6],unname(stat[5]-stat[6]),stat[7:8],unname(stat[8]-stat[7]))
names(stat)[c(5,8,11)]<-c("Corl-Coru","Pl-Pu","D2u-D2l")

#get surrogates and get stats for them, preserving kendall
cop<-normalCopula(.5,2)
numsurrog<-1000
surv<-copsurrog2d(v,cop,"kendall",numsurrog)
statsurr_k<-matrix(NA,length(stat),numsurrog)
rownames(statsurr_k)<-names(stat)
for (counter in 1:dim(surv)[3])
{
  h<-stat_flexible_fn(m=surv[,,counter],lb=0,ub=0.1)
  h<-unlist(h)
  h<-c(h[1:4],h[3]-h[4],h[5:6],h[5]-h[6],h[7:8],h[8]-h[7])
  statsurr_k[,counter]<-unname(h)
}

#same, preserving spearman
surv<-copsurrog2d(v,cop,"spearman",numsurrog)
statsurr_s<-matrix(NA,length(stat),numsurrog)
rownames(statsurr_s)<-names(stat)
for (counter in 1:dim(surv)[3])
{
  h<-stat_flexible_fn(m=surv[,,counter],lb=0,ub=0.1)
  h<-unlist(h)
  h<-c(h[1:4],h[3]-h[4],h[5:6],h[5]-h[6],h[7:8],h[8]-h[7])
  statsurr_s[,counter]<-unname(h)
}
```

@@

```{r stat_aphid_count, echo=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("CopulaFunctions.R"),mtime("CopulaFunctions_flexible.R"),mtime("NonParamStat.R"))}
set.seed(seed) 
resloc<-"./Results/stat_results/stat_aphid_count/"

@@

@@

@@

```{r stat_aphid_ff, echo=F, cache=T, cache.extra=list(seed,data_aphid_ff,mtime("CopulaFunctions.R"),mtime("CopulaFunctions_flexible.R"),mtime("NonParamStat.R"))}

set.seed(seed)
resloc<-"./Results/stat_results/stat_aphid_ff/"

@@

@@

@@

### Non-paramtric analysis of tail dependence
```{r stat_plankton_north_sea, echo=F, cache=T, cache.extra=list(seed,data_plankton_north_sea,mtime("CopulaFunctions.R"),mtime("CopulaFunctions_flexible.R"),mtime("NonParamStat.R"))}

set.seed(seed)
resloc<-"./Results/stat_results/stat_plankton_north_sea/"

@@

@@
